Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Editorial fixes throughout

   \item Once the connection is established, the receiver
     then indicates its media play-out delay, in milliseconds, via
     the \texttt{set\_po\_delay()} call. This specifies the time that the
     application will buffer data, to compensate for network timing jitter,
     before it is rendered to the user. The play-out delay is fed back to
     the sender host, for use as part of the media deadline estimation.

@@

    The \texttt{recv\_message()} call returns the sequence number, dependency
    information, and sub-stream identifier along with any received message,
    allowing the receiver to direct it to the correct decoding queue.

@@

The implication of this reality is that it is difficult to deploy new
transport protocols. The installed base of NATs, firewalls, and other
middleboxes is such that packets that do not look like TCP or UDP are
unlikely to pass the network. We may innovate all we like, provided the
transport of the future looks like TCP or UDP to middleboxes.\footnote{
  This is inconvenient, certainly, but is not necessarily a bad thing.
  The Internet is critical infrastructure. It support emergency services,
  healthcare applications, infrastructure components, financial services,
  and so on, many of which are essential to the functioning of society.
  Making changes to this type of infrastructure \emph{should} require
  careful backwards compatibility \cite{mcquistin:2015:reinterpreting}.
}

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency, although it is known to be less
aggressive than standard TCP, and is prone to starvation; FAST TCP 
\cite{jin:2004:fast-tcp} is a more modern delay-based algorithm that 
competes well with standard TCP in many environments, and is seeing 
commercial deployment.  The development of TCP congestion control shows
that there might be fairness issues as new algorithms are deployed, but the
network does not prevent the deployment of those algorithms.

@@

%==================================================================================================
%\section{Acknowledgements}
%
% Acknowledge funding sources.
%
%==================================================================================================
\balance
\bibliographystyle{abbrv}
\bibliography{paper}
\end{document}
% vim: set ts=2 sw=2 tw=75 et ai:

>>>>

   \item Once the connection is established, the receiver
     then indicates its media play-out delay, in milliseconds, via
     the \texttt{set\_po\_delay()} call. This specifies the time that the
     application will buffer data, to compensate for network timing jitter,
     before it is rendered to the user. The play-out delay is fed back to
     the sender, for use as part of the media deadline estimation.

@@

    The \texttt{recv\_message()} call returns the sequence number, dependency
    information, and sub-stream identifier along with any received message.
    This allows the receiver to direct the message to the correct decoding queue.

@@

The implication of this reality is that it is difficult to deploy new
transport protocols. The installed base of NATs, firewalls, and other
middleboxes is such that packets that do not look like TCP or UDP are
unlikely to pass the network. We may innovate all we like, provided the
transport of the future looks like TCP or UDP to middleboxes.
  This is inconvenient, certainly, but is not necessarily a bad thing.
  The Internet is critical infrastructure. It support emergency services,
  healthcare applications, infrastructure components, financial services,
  and so on, many of which are essential to the functioning of society.
  Making changes to this type of infrastructure \emph{should} require
  careful consideration of backwards compatibility \cite{mcquistin:2015:reinterpreting}.

@@

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency, although it is known to be less
aggressive than standard TCP, and is prone to starvation. FAST TCP 
\cite{jin:2004:fast-tcp} is a more modern delay-based algorithm that 
competes well with standard TCP in many environments, and is seeing 
commercial deployment.  The development of TCP congestion control shows
that there might be fairness issues as new algorithms are deployed, but the
network does not prevent the deployment of those algorithms.

@@

%==================================================================================================
%\section{Acknowledgements}
%
% Acknowledge funding sources.
%
%==================================================================================================
\balance
\bibliographystyle{acm}
\bibliography{paper}
\end{document}
% vim: set ts=2 sw=2 tw=75 et ai:
